Discovering Focused Microgenre Communities

### 2023-08-03 main.tex

\begin{figure}[ht!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy3.png}
        \caption{Edge similarity matrix from toy example.}
        \label{fig:link-toy3}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy4.png}
        \caption{Edge distance matrix from toy example.}
        \label{fig:link-toy4}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy5.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy5}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy}
 \end{figure}

@@

\begin{figure}[ht!]
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro-labels.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro-labels}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro.png}
        \caption{c = 3, k = 102}
        \label{fig:dend-micro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro-labels.png}
        \caption{c = 3, k = 102}
        \label{fig:dend-micro-labels}
    \end{subfigure}
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/classic-rock-branches.png}
        \caption{c = 3, k = 12}
        \label{fig:dend-micro-classic-rock}
    \end{subfigure} 
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/blues-branches.png}
        \caption{c = 3, k = 5}
        \label{fig:dend-micro-blues}
    \end{subfigure}
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/opera-branches.png}
        \caption{c = 3, k = 2}
        \label{fig:dend-micro-opera}
    \end{subfigure}
    \caption{}
    \label{fig:dend}
 \end{figure}

>>>>

\begin{figure}[ht!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{fig:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{fig:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}

@@

\begin{figure}[ht!]
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro-labels.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro-labels}
    \end{subfigure} 
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/classic-rock-branches.png}
        \caption{c = 3, k = 12}
        \label{fig:dend-micro-classic-rock}
    \end{subfigure} 
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/blues-branches.png}
        \caption{c = 3, k = 5}
        \label{fig:dend-micro-blues}
    \end{subfigure}
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/opera-branches.png}
        \caption{c = 3, k = 2}
        \label{fig:dend-micro-opera}
    \end{subfigure}
    \caption{}
    \label{fig:dend}
 \end{figure}
